Local-to-Global Mariculture Modelling

### 2025-12-18 docs-working/05_formulating_feeds.qmd
Updates to feeds documentation

>>>>

# Comparing feeds

The three "biomar" feeds were designed to be isoenergetic.

```{r feed-stats}
#| code-summary: Calculate some stats about the feeds

feed_stats <- feed_inputs %>% 
  select(-contains(c("max", "min"))) %>% 
  mutate(
    ing_protein = proportion * protein,
    ing_carb = proportion * carb,
    ing_lipid = proportion * lipid,
    digest_protein = ing_protein * protein_digestibility,
    digest_carb = ing_carb * carb_digestibility,
    digest_lipid = ing_lipid * lipid_digestibility,
    E_protein = digest_protein * 17,
    E_carb = digest_carb * 16.8,
    E_lipid = digest_lipid * 37.6
  ) %>% 
  group_by(feed) %>% 
  reframe(
    total_protein = sum(ing_protein),
    total_carb = sum(ing_carb),
    total_lipid = sum(ing_lipid),
    AD_protein = sum(digest_protein),
    AD_carb = sum(digest_carb),
    AD_lipid = sum(digest_lipid),
    E_protein = sum(E_protein),
    E_carb = sum(E_carb),
    E_lipid = sum(E_lipid)
    ) %>% 
  mutate(
    E = E_protein + E_carb + E_lipid,
    group = case_when(str_detect(feed, "biomar") ~ "biomar", T ~ "other")
  ) %>% 
  relocate(group, .before = "feed") %>% 
  arrange(group)

feed_stats %>% 
  select(group, feed, E)
```

```{r feed-macro-digestibility}
#| code-summary: Code to generate plot
#| fig-cap: Total protein, carbohydrate and lipid composition of each feed, with the undigestible portion shown as the lighter bars on top.

merge(
  feed_stats %>% 
    select(feed, group, contains("total_")) %>% 
    pivot_longer(
      cols = contains("total"),
      names_to = "macro", names_prefix = "total_",
      values_to = "total"
    ),
  feed_stats %>% 
    select(feed, group, contains("AD_")) %>% 
    pivot_longer(
      cols = contains("AD"),
      names_to = "macro", names_prefix = "AD_",
      values_to = "AD"
    ),
  by = c("feed", "group", "macro")
  ) %>% 
  mutate(feed = as.factor(feed)) %>%   
  ggplot(aes(x = macro, fill = feed)) +
  geom_col(aes(y = total), position = position_dodge(), alpha = 0.5, colour = "black") +
  geom_col(aes(y = AD), position = position_dodge(), alpha = 0.75, colour = "black") +
  theme_classic() +
  facet_wrap(facets = vars(group))
```

```{r feed-energy}
#| code-summary: Code to generate plot
#| fig-cap: The proportion of energy derived from protein, carbohydrate and lipid within each feed.

feed_stats %>% 
  mutate(
    E_protein = E_protein/E,
    E_carb = E_carb/E,
    E_lipid = E_lipid/E
  ) %>% 
  select(feed, group, contains("E_")) %>% 
  pivot_longer(
    cols = contains("E_"),
    names_to = "macro", names_prefix = "E_",
    values_to = "value"
  ) %>% 
  ggplot(aes(x = macro, y = value, fill = feed)) +
  geom_col(position = position_dodge(), colour = "black") +
  theme_classic() +
  facet_wrap(facets = vars(group))
```

### 2025-12-18 docs-working/08_data_analysis.qmd
Updates to feeds documentation

```{r raw-outputs}
total_ends <- qread(file.path(output_model_farm_path, "total_ends.qs")) %>% 
  mutate(
    feed_group = as.factor(str_remove(feed, "_min|_max")),
    feed_type = case_when(
      str_detect(feed, "_min") ~ "min",
      str_detect(feed, "_max") ~ "max",
      T ~ "mean"
    ) %>% as.factor(),
    mean = set_units(mean, "g"),
    sd = set_units(sd, "g"),
    mean_biomass = set_units(mean, "g g_fish-1"),
    sd_biomass = set_units(sd, "g g_fish-1")
  )

cohort_results <- qread(file.path(output_model_cohort_path, "cohort_results.qs")) %>% 
  mutate(
    feed_group = as.factor(str_remove(feed, "_min|_max")),
    feed_type = case_when(
      str_detect(feed, "_min") ~ "min",
      str_detect(feed, "_max") ~ "max",
      T ~ "mean"
    ) %>% as.factor()
  )
```

>>>>

```{r raw-outputs}
total_ends <- file.path(output_model_farm_path, "total_ends.qs") %>% 
  qread() %>% 
  mutate(
    feed_group = factor(
      str_remove(feed, "_min|_max"), 
      levels = long_feeds,
      labels = short_feeds
      ),
    feed_type = case_when(
      str_detect(feed, "_min") ~ "min",
      str_detect(feed, "_max") ~ "max",
      T ~ "mean"
      ) %>% as.factor(),
    mean = set_units(mean, "g"),
    sd = set_units(sd, "g"),
    mean_biomass = set_units(mean_biomass, "g g_fish-1"),
    sd_biomass = set_units(sd_biomass, "g g_fish-1")
  )

cohort_results <- file.path(output_model_cohort_path, "cohort_results.qs") %>% 
  qread() %>% 
  mutate(
    feed_group = factor(
      str_remove(feed, "_min|_max"), 
      levels = long_feeds,
      labels = short_feeds
      ),
    feed_type = case_when(
      str_detect(feed, "_min") ~ "min",
      str_detect(feed, "_max") ~ "max",
      T ~ "mean"
      ) %>% as.factor(),
    mean = set_units(mean, "g"),
    sd = set_units(sd, "g"),
    mean_biomass = set_units(mean_biomass, "g g_fish-1"),
    sd_biomass = set_units(sd_biomass, "g g_fish-1")
  )
```

### 2025-12-18 docs-working/index.qmd
Updates to feeds documentation

farm_locs <- find_read(output_farm_data_path, "geometry") %>% 
  rename(farm_ID = farm_id) %>% 
  mutate(country = as.factor(country))
countries_long <- farm_locs %>%
  mutate(
    longitude = map_dbl(geometry, ~st_coordinates(.x)[1]),
    latitude = map_dbl(geometry, ~st_coordinates(.x)[2])
  ) %>% 
  st_drop_geometry() %>% 
  group_by(country) %>% 
  reframe(latitude = mean(latitude)) %>% 
  arrange(-latitude) %>% 
  pull(country) %>% 
  as.character() 
countries_short <- countries_long %>% 
  str_replace("United States of America", "USA") %>% 
  str_replace("Russian Federation", "Russia") %>% 
  str_replace("United States of America", "USA")
farm_locs <- farm_locs %>% 
  mutate(
    country = factor(
      country, 
      levels = countries_long,
      labels = countries_short
    ))

long_feeds <- c("marine_dominant", "plant_dominant", "novel_inclusive")
short_feeds <- c("MD", "PD", "NI")

feed_pal <- c(
  "past" = "#E41A1C", 
  "reference" = "#377EB8", 
  "future" = "#4DAF4A",
  "plant_dominant" = "#4DAF4A",
  "marine_dominant" = "#377EB8",
  "novel_inclusive" = "#E41A1C",
  "PD" = "#4DAF4A",
  "MD" = "#377EB8",
  "NI" = "#E41A1C"
)
cohort_pal <- c("1" = "#E41A1C", "2" = "#377EB8", "3" = "#4DAF4A", "all" = "black")
macro_pal <- c(
  "protein" = "darkred", 
  "P" = "darkred", 
  "carbohydrates" = "steelblue", 
  "C" = "steelblue", 
  "lipids" = "darkgoldenrod1", 
  "L" = "darkgoldenrod1"
)

prettyplot <- function() {
  theme_classic() +
    theme(
      text = element_text(family = "serif", size = 14, colour = "black"),
      legend.position = "none",
      axis.title.y = element_text(margin = margin(r = 5)),
      axis.title.x = element_text(margin = margin(t = 5))
    )
}
```

>>>>

farm_locs <- find_read(output_farm_data_path, "geometry") %>% 
  rename(farm_ID = farm_id) %>% 
  mutate(country = as.factor(country))
countries_long <- farm_locs %>%
  mutate(
    longitude = map_dbl(geometry, ~st_coordinates(.x)[1]),
    latitude = map_dbl(geometry, ~st_coordinates(.x)[2])
  ) %>% 
  st_drop_geometry() %>% 
  group_by(country) %>% 
  reframe(latitude = mean(latitude)) %>% 
  arrange(-latitude) %>% 
  pull(country) %>% 
  as.character() 
countries_short <- countries_long %>% 
  str_replace("United States of America", "USA") %>% 
  str_replace("Russian Federation", "Russia") %>% 
  str_replace("United States of America", "USA")
farm_locs <- farm_locs %>% 
  mutate(
    country = factor(
      country, 
      levels = countries_long,
      labels = countries_short
    ))
```
